Keep your Laziness in Check

### 2018-01-31 paper/main.tex
Some work on the intro

Lazy evaluation brings tremendous power to modularization of functional
programming ~\cite{WhyFPMatters}. Haskell is one of the most popular programming
languages that gives its programmers the power of lazy evaluation.

>>>>

\leo{Point of first paragraph: lazy evaluation is powerful}

Lazy evaluation brings tremendous power to modularization of
functional programming ~\cite{WhyFPMatters} and is actively used in
various practical applications. For instance, the big-data framework
Spark uses laziness to drive computations on demand\cn, Apple's
programming language Swift leverages it to initialize expensive
resources as needed\cn, and many functional reactive programming web
frameworks rely on it\cn \leo{This point might need more exposition
about frp}. Haskell is the most popular programming language that
allows programmers to enjoy the power of lazy evaluation by default.

\leo{Point of second paragraph: lazy evaluation is hard}

\leo{I'm sorry in advance for the following sentence. It was just too tempting.}
\begin{itemize}
\item Unfortunately, such power comes with great responsibility.\leo{-Ben
Parker :P}
\item Reasoning about lazy programs is notoriously hard, because
it is difficult to predict if and when thunks are evaluated.
\item Moreover, there is \leo{currently?} no way to specify or check the expected
laziness behavior of a function.
\item That would be good.
\end{itemize}

\leo{Example 1: Okasaki queues}
As a first example of Laziness being both useful and error-prone, we can turn to
purely functional data structures\cn, and in particular queues.
\leo{Summarize queue example}

\leo{Example 2: Knapsack}
